PS753 Glossary

### 2022-02-08 _academics/ps753-glossary/ps753-glossary.Rmd
build

<p style="background: #eee">
Academics &gt; [PS 753](../ps753/index.html)
&gt; Glossary
</p>

@@

## Week 1

@@

two-mode data
: ties between different sets (or categories) of agents, such as ties between nations and international organizations

@@

## Week 2

@@

>>>>

<p style="background: #eee">
[<i class="fas fa-home"></i>](/) &gt; Academics &gt; [PS 753](../ps753/index.html)
&gt; Glossary
</p>

@@

## Week 1 - Introduction

@@

two-mode data / bipartite data
: ties between different sets (or categories) of agents, such as ties between nations and international organizations

@@

## Week 2 - Network Structure

@@

## Week 3 - Network Degree

### Class lecture 3a: [Degree](https://www.loom.com/share/49273add09ce4b26924b7f5ab2983810)

degree
: the number of links that a node has; the number of nodes it's connected to

degree distribution
: a distribution showing the number of nodes of a network that have each degree level

indegree
: the number of links that a node *receives* in a directed network

outdegree
: the number of links that a node *sends* in a directed network

### Class lecture 3b: [Centrality vs. Centralization](https://www.loom.com/share/d2ed1cbb9bc84d27adfbb3febedfeac4)

centrality
: a measure of the prominence of one node relative to others; can be variously defined

(degree) centrality
: proportional the the number of other nodes to which a node is linked

centralization
: a property of a graph, referring to its overall cohesion; comparing most central point to all other points; ratio of the actual sum of differences to the maximum possible sum of differences

### Class lecture 3c: [Network Density](https://www.loom.com/share/6e43e1fca3d44e1881f1a1d4895c26d3)

network density
: number of ties as a proportion of the maximum possible number of ties; varies from 0 to 1, calculation will vary by whether network is undirected or directed (twice as many potential connections)
